Near Optimal Behavior with Approximate State Abstraction

### 2016-02-04 paper/results_discussion.tex
Some random results discussion push

Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}. Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both fall off dramatically. We attribute the sudden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable. Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent. Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost in the state aggregation.

>>>>

Our experimental results also highlight a noteworthy characteristic of approximate state abstraction in goal-based \acp{MDP}. Taxi exhibits relative stability in state space size and behavior for epsilon up to $.02$ until both fall off dramatically. We attribute the sugdden fall off in number of abstract states and value of the derived policy in Taxi to its goal-based nature; once information critical for achieving optimal behavior is lost in the state aggregation, solving the goal -- and so acquiring any reward -- is unattainable. Conversely, in the Random domain, a great deal of near-optimal policies are available to the agent. Thus, even the information for optimal behavior is lost with an increase in $\epsilon$ there are a great deal of near-optimal policies available to the agent which are not lost in the state aggregation.
